---
title: "Ergodicity"
output: 
  bookdown::html_document2:
    toc_depth: 2
    theme: cosmo
    df_print: kable
---
#setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#install packages
```{r,message=F}
install.packages("psychometric")
```

#load libraries
```{r,message=F}
library(tibble)
library(tidyr)
library(readr)
library(ggplot2)
library(dplyr)
library(readxl)
library(rmcorr)
library(bookdown)
library(rmcorr)
library(psychometric)
```

#load data set (data set = not original, but the one where there is load data of one day and recovery data of the next day)
```{r}
Resilience <- read.csv(file =                  "C:\\Users\\Neuma\\surfdrive\\Shared\\anonymous_processed_output\\simulation_data_Niklas\\preprocessed_1day_history.csv")
head(Resilience, 5)
```

#Data set with no NAs (for EMH and LOAD)
```{r}
NoNAs <- Resilience %>%
  filter(!is.na(EMH_1st_session_first_fut_01_trainingdays), !is.na(LOAD_sum_prev_01_days))
head(NoNAs, 5)
```
```{r}
sort(table(NoNAs$Speler))
```

#Select Team 1f 
```{r}
OneF <- NoNAs%>%
  filter(Team == "1f63943fcc3909be531e7939840ac071") #33 players in 1f

sort(table(OneF$Speler))
table(OneF$day_count)
glimpse(OneF$Speler)
```

#make every day_count to an ongoing number string and delete double dates
```{r}
OneFCount <- transform(OneF, new_day_count=as.numeric(factor(day_count)))
```

#Create a function which can for some start date i and for some number of days j get the subset we want

```{r, warning=F}
subset_detection <- function(startdate, ndays) {
  df <- OneFCount %>%
    filter(new_day_count >= startdate & new_day_count < startdate + ndays) %>%
    count(Speler) %>%
    filter(ndays == n)
  nrow(df)
}
subset_detection(1, 3)

```
```{r}
n_subset <- function(startdate) {
  previous <- 2
  ndays <- 0
  while (ndays <= previous) {
    ndays <- ndays + 1
    previous <- subset_detection(startdate, ndays)
    #print(paste(ndays, ":", previous))
    
  }
  if (ndays == previous){
    ndays
  } else {
    ndays - 1
  }
}
#n_subset
#for (i in 1:313){
 #print(n_subset(i))
#}
A <- purrr::map(1:313, n_subset)
```
```{r}
max(unlist(A))
```

```{r}
df2 <- tibble(Index = 1:313, result = unlist(A))
df2 %>% arrange(result)
```

```{r} 
df <- tribble(
  ~Speler, 
  "a", 
  "a",
  "b"
)
df %>% count(Speler)
```
###
```{r}
table(OneFCount$new_day_count)
```

```{r}
OneFPeriod <- OneFCount %>%
  filter(new_day_count >193 & new_day_count < 204) %>%
  filter(Speler != "98f56f89a69c8dd014e38f8748d4d0f9") %>%
  filter(Speler != "2c2d73d534bf7d347d3ba20a8b19643f") %>%
  filter(Speler != "b99679d13454f4e469fa212cf0fd3395") %>%
  filter(Speler != "f5f2d6b7f2630346f45fd41324d85a0c") %>%
  filter(Speler != "18f141d875cf6d722a187236cfa4482e") %>%
  filter(Speler != "9e3524149a64c395f150c26dbf9f970d") %>%
  filter(Speler != "343dfbbcb3cf7a3869a8ea628cd880f1")

sort(table(OneFPeriod$Speler))
```

#Central Tendencies AggAn1f and AnAgg1f
```{r}
AggAn1f <- OneFPeriod %>%
  group_by(day_count) %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))

MeanAggAn1f <- AggAn1f %>%
  summarise(mean(meanEMH), mean(meanLOAD), mean(sdEMH), mean(sdLOAD), mean(medianEMH), mean(medianLOAD))

AnAgg1f <- OneFPeriod %>%
  group_by(Speler) %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))

MeanAnAgg1f <- AnAgg1f %>%
  summarise(mean(meanEMH), mean(meanLOAD), mean(sdEMH), mean(sdLOAD), mean(medianEMH), mean(medianLOAD))

Allatonce1f <- OneFPeriod %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))
```

#Correlation AggAn1f and AnAgg1f
```{r}
CorrAggAn1f <- OneFPeriod %>%
  group_by(day_count) %>%
  summarize(N = n(), r = cor(LOAD_sum_prev_01_days, EMH_1st_session_first_fut_01_trainingdays, use = "pairwise.complete.obs", method = "spearman"))

MeanCorrAggAn1f <- CorrAggAn1f %>%
  filter(!is.na(r)) %>%
  summarise(mean(r), sd(r), median(r)) 

CIr(r = -0.1391591, n = 10, level = .95) #How to calc CIs for every single day?

#this is the inter-individual approach all at once
spearman1f <- cor.test(OneFPeriod$LOAD_sum_prev_01_days, OneFPeriod$EMH_1st_session_first_fut_01_trainingdays, method = "spearman")

CIr(r = -0.2814702, n = 10, level = .95)

#this now is the intra-individual approach with rmcorr
rmcorr <- rmcorr(Speler, EMH_1st_session_first_fut_01_trainingdays, LOAD_sum_prev_01_days_noMissing, OneFPeriod)

#this is how I could calc the CI for every individual speler
rmcorr(Speler == "dbbd087c3555a335d446c0490499ad78"	, EMH_1st_session_first_fut_01_trainingdays, LOAD_sum_prev_01_days_noMissing, OneFPeriod)

#this is the intra-individual analysis with pearson method (same result, but also provides SDs for overall and each individual)
CorrAnAgg1f <- OneFPeriod %>%
  group_by(Speler) %>%
  summarize(N = n(), r = cor(LOAD_sum_prev_01_days, EMH_1st_session_first_fut_01_trainingdays, use = "pairwise.complete.obs", method = "pearson"))

MeanCorrAnAgg1f <- CorrAnAgg1f %>%
  filter(!is.na(r)) %>%
  summarise(mean(r), sd(r), median(r)) 
```

```{r}
hg1fAgg <- hist(CorrAggAn1f$r, breaks = 10)

hg1fAn <- hist(CorrAnAgg1f$r, breaks = 6)

range(c(hg1fAgg$breaks, hg1fAn$breaks))

max(c(hg1fAgg$count, hg1fAn$count))

plot(hg1fAgg, col = rgb(1,0,0,0.4), main = "Correlation of load and recovery for the U17 Team", xlab = "Correlation", xlim = c(-1, 1), ylim = c(0, 5), xaxt = "n")
plot(hg1fAn, add = TRUE, col = rgb(0,0,1,0.4))
plot(hg1fAgg, col = rgb(1,0,0,0.4), add = T)
#plot(hg1fAn, col = rgb(1,0,0,0.4), add = T)
axis(1, at = seq(-1, 1, by = 0.2), las = 2)
legend("topright", c("Intraindividual, SD = .26", "Interindividual, SD = .46"),
       fill = c(rgb(0,0,1,0.4), rgb(1,0,0,0.4)))
abline(v = MeanCorrAggAn1f$`mean(r)`, col = rgb(0,0,1,1/4)) #line mean corr. Group
abline(v = MeanCorrAnAgg1f$`mean(r)`, col = rgb(1,0,0,1/4)) #line mean corr. indiv.
abline(v = MeanCorrAggAn1f$`median(r)`, col = rgb(0,0,1,1/4), lty = 2) #line mean median corr. group
abline(v = MeanCorrAnAgg1f$`median(r)`, col = rgb(1,0,0,1/4), lty = 2) #line mean median corr.indiv
```

#Select Team 2d
```{r}
TwoD <- NoNAs%>%
  filter(Team == "2d64fe64ed4b5f2d59ffbd31501cd294") #33 players in 2d

sort(table(TwoD$Speler))
table(TwoD$day_count)
glimpse(TwoD$Speler)
```

#make every day_count to an ongoing number string and delete double dates
```{r}
TwoDCount <- transform(TwoD, new_day_count=as.numeric(factor(day_count)))
```

#Create a function which can for some start date i and for some number of days j get the subset we want

```{r, warning=F}
subset_detection <- function(startdate, ndays) {
  df <- TwoDCount %>%
    filter(new_day_count >= startdate & new_day_count < startdate + ndays) %>%
    count(Speler) %>%
    filter(ndays == n)
  nrow(df)
}
subset_detection(1, 3)

```
```{r}
n_subset <- function(startdate) {
  previous <- 2
  ndays <- 0
  while (ndays <= previous) {
    ndays <- ndays + 1
    previous <- subset_detection(startdate, ndays)
    #print(paste(ndays, ":", previous))
    
  }
  if (ndays == previous){
    ndays
  } else {
    ndays - 1
  }
}
#n_subset
#for (i in 1:312){
 #print(n_subset(i))
#}
A <- purrr::map(1:312, n_subset)
```
```{r}
max(unlist(A))
```

```{r}
df2 <- tibble(Index = 1:312, result = unlist(A))
df2 %>% arrange(result)
```

```{r} 
df <- tribble(
  ~Speler, 
  "a", 
  "a",
  "b"
)
df %>% count(Speler)
```
###
```{r}
table(TwoDCount$new_day_count)
```


```{r}
TwoDPeriod <- TwoDCount %>%
  filter(new_day_count >194 & new_day_count < 210) %>%
  filter(Speler != "399e92d3c291705db2be47ce416b25b7") %>%
  filter(Speler != "a09bd414dc32b9f5b1fabd1e30969298") %>%
  filter(Speler != "e2adca493c7d8b834ebafacef3d2c446") %>%
  filter(Speler != "65083f4fcf0fea29bdcb79b0474be7fc") %>%
  filter(Speler != "067c541b77e73206d543bad5362d28f3") 

sort(table(TwoDPeriod$Speler))
```

#Central Tendencies AggAn2d and AnAgg2d
```{r}
AggAn2d <- TwoDPeriod %>%
  group_by(day_count) %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))

MeanAggAn2d <- AggAn2d %>%
  summarise(mean(meanEMH), mean(meanLOAD), mean(sdEMH), mean(sdLOAD), mean(medianEMH), mean(medianLOAD))

AnAgg2d <- TwoDPeriod %>%
  group_by(Speler) %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))

MeanAnAgg2d <- AnAgg2d %>%
  summarise(mean(meanEMH), mean(meanLOAD), mean(sdEMH), mean(sdLOAD), mean(medianEMH), mean(medianLOAD))
```
#Correlation AggAn2d and AnAgg2d
```{r}
CorrAggAn2d <- TwoDPeriod %>%
  group_by(day_count) %>%
  summarize(N = n(), r = cor(LOAD_sum_prev_01_days, EMH_1st_session_first_fut_01_trainingdays, use = "pairwise.complete.obs", method = "spearman")) 

MeanCorrAggAn2d <- CorrAggAn2d %>%
  filter(!is.na(r)) %>%
  summarise(mean(r), sd(r), median(r)) 

CIr(r = -0.0362162, n = 15, level = .95) #How to calc CIs for every single day?

#this is the inter-individual approach all at once
spearman2d <- cor.test(TwoDPeriod$LOAD_sum_prev_01_days, TwoDPeriod$EMH_1st_session_first_fut_01_trainingdays, method = "spearman")

CIr(r = -0.07298894, n = 15, level = .95)

#this now is the intra-individual approach with rmcorr
rmcorr(Speler, EMH_1st_session_first_fut_01_trainingdays, LOAD_sum_prev_01_days_noMissing, TwoDPeriod)

#see under Team 1f how to calc the CI and SDs for every single player
```





#Select Team 8f 
```{r}
EightF <- NoNAs%>%
  filter(Team == "8f5a6405211400c9e4befdc9f184046b") #36 players in 8f

sort(table(EightF$Speler))
table(EightF$day_count)
glimpse(EightF$Speler)
```

#make every day_count to an ongoing number string and delete double dates
```{r}
EightFCount <- transform(EightF, new_day_count=as.numeric(factor(day_count)))
```

#Create a function which can for some start date i and for some number of days j get the subset we want

```{r, warning=F}
subset_detection <- function(startdate, ndays) {
  df <- EightFCount %>%
    filter(new_day_count >= startdate & new_day_count < startdate + ndays) %>%
    count(Speler) %>%
    filter(ndays == n)
  nrow(df)
}
subset_detection(1, 3)

```
```{r}
n_subset <- function(startdate) {
  previous <- 2
  ndays <- 0
  while (ndays <= previous) {
    ndays <- ndays + 1
    previous <- subset_detection(startdate, ndays)
    #print(paste(ndays, ":", previous))
    
  }
  if (ndays == previous){
    ndays
  } else {
    ndays - 1
  }
}
#n_subset
#for (i in 1:393){
 #print(n_subset(i))
#}
A <- purrr::map(1:393, n_subset)
```
```{r}
max(unlist(A))
```

```{r}
df2 <- tibble(Index = 1:393, result = unlist(A))
df2 %>% arrange(result)
```

```{r} 
df <- tribble(
  ~Speler, 
  "a", 
  "a",
  "b"
)
df %>% count(Speler)
```
###
```{r}
table(EightFCount$new_day_count)
```

```{r}
EightFPeriod <- EightFCount %>%
  filter(new_day_count >1 & new_day_count < 13) %>%
  filter(Speler != "d272a44ec19af13a6e47ef361e6071b0") %>%
  filter(Speler != "025f95604ee430a65b888f366737e812") %>%
  filter(Speler != "e725fa22afa5ddd4b7bb4a13024f30b0") %>%
  filter(Speler != "9ef04893710a7b946f5c8e8c32d2f2e5") %>%
  filter(Speler != "2cf758b642c5bcb6dd50e13470b008d8") %>%
  filter(Speler != "854284d212f5c0ea2ee3cdc02f235c79") %>%
  filter(Speler != "3e2e85f3c9e0d6491dba2758c2e70c38") 

sort(table(EightFPeriod$Speler))
```

#Central Tendencies AggAn1f and AnAgg1f
```{r}
AggAn8f <- EightFPeriod %>%
  group_by(day_count) %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))

MeanAggAn8f <- AggAn8f %>%
  summarise(mean(meanEMH), mean(meanLOAD), mean(sdEMH), mean(sdLOAD), mean(medianEMH), mean(medianLOAD))

AnAgg8f <- EightFPeriod %>%
  group_by(Speler) %>%
  summarise(meanEMH = mean(EMH_1st_session_first_fut_01_trainingdays), meanLOAD = mean(LOAD_sum_prev_01_days), sdEMH = sd(EMH_1st_session_first_fut_01_trainingdays), sdLOAD = sd(LOAD_sum_prev_01_days), medianEMH = median(EMH_1st_session_first_fut_01_trainingdays), medianLOAD = median(LOAD_sum_prev_01_days))

MeanAnAgg8f <- AnAgg8f %>%
  summarise(mean(meanEMH), mean(meanLOAD), mean(sdEMH), mean(sdLOAD), mean(medianEMH), mean(medianLOAD))
```

#Correlation AggAn8f and AnAgg8f
```{r}
CorrAggAn8f <- EightFPeriod %>%
  group_by(day_count) %>%
  summarize(N = n(), r = cor(LOAD_sum_prev_01_days, EMH_1st_session_first_fut_01_trainingdays, use = "pairwise.complete.obs", method = "spearman")) 

MeanCorrAggAn8f <- CorrAggAn8f %>%
  filter(!is.na(r)) %>%
  summarise(mean(r), sd(r), mean(median)) 

CIr(r = -0.1669229, n = 11, level = .95) #How to calc CIs for every single day?

#this is the inter-individual approach all at once
spearman8f <- cor.test(EightFPeriod$LOAD_sum_prev_01_days, EightFPeriod$EMH_1st_session_first_fut_01_trainingdays, method = "spearman")

CIr(r = 0.04192393, n = 11, level = .95)

#this now is the intra-individual approach with rmcorr
rmcorr(Speler, EMH_1st_session_first_fut_01_trainingdays, LOAD_sum_prev_01_days_noMissing, EightFPeriod)

#see under Team 1f how to calc the CI and SDs for every single player
```
#load data of simulation data
```{r}
Simulation <- read.csv(file =                  "C:\\Users\\Neuma\\surfdrive\\Shared\\anonymous_processed_output\\simulation_data_Niklas_v2\\safe_to_share\\simulation_data_REAL_group_effect.csv")
head(Simulation, 5)
glimpse(Simulation$Speler)
```
#Data set with no NAs (for EMH and LOAD)
```{r}
NoNAsSim <- Simulation %>%
  filter(!is.na(EMH_1st_session_first_fut_01_trainingdays), !is.na(LOAD_sum_prev_01_days))
head(NoNAsSim, 5)
```
#make every day_count to an ongoing number string and delete double dates
```{r}
SimDays <- transform(NoNAsSim, new_day_count=as.numeric(factor(day_count)))
```